Firstly, I would like to express my sincere gratitude to my advisor Prof.$\rule{3cm}{0.3mm}$ for the continuous support of my Ph.D/Master study and related research, for his patience, motivation, and immense knowledge. His guidance helped me in all the time of research and writing of this thesis. I could not have imagined having a better advisor and mentor for my Ph.D/Master study.

Besides my advisor, I would like to thank the rest of my thesis committee: Prof. $\rule{2cm}{0.3mm}$, Prof. $\rule{3cm}{0.3mm}$, and Dr. $\rule{3cm}{0.3mm}$, for their insightful comments and encouragement, but also for the hard question which lightened me to widen my research from various perspectives.

My sincere thanks also goes to Dr. $\rule{3cm}{0.3mm}$, Dr. $\rule{3cm}{0.3mm}$, and Dr. $\rule{3cm}{0.3mm}$, who provided me an opportunity to join their team as intern, and who gave access to the laboratory and research facilities. Without they precious support it would not be possible to conduct this research.

I thank my fellow lab-mates in for the stimulating discussions, for the sleepless nights we were working together before deadlines, and for all the fun we have had in the last few years. Also I thank my friends in the following institution $\rule{3cm}{0.3mm}$ . In particular, I am grateful to Dr. $\rule{3cm}{0.3mm}$ for enlightening me the first glance of research.

Last but not the least, I would like to thank my family: my parents and to my brothers and sister for supporting me spiritually throughout writing this thesis and my my life in general.